Disc stuff

### 2012-09-27 paper.tex
Figures

 \caption{enevlope model with temp and dust temp (red, green) in kelvin, log number density (blue) in cm$^{-1}$ and inward velocity$\times$100 (cyan) in m$\,$s$^{-1}$}
\end{figure}

@@

-describe the chemistry  - refer to Ilee et al. which have been taken as input to the rad transf (RT) code
Chemical abundances in the disc were taken from Ilee et. al (2011) which followed the changes of chemical abundances of trace particles moving through the disc as it evolved. The abundances of 125 speices related by 1334 reactions where followed through the time evoltion of the disc. These abundances ware interpolated onto a 51$^3$ grid covering the disc with cells of size 2.2$\times$2.2$\times$0.22$\,$au. Abundances in the envelope model were as follows:\newline

tableify ?
HCO$^+$: as the H2O profile from ??? scaled so that the maximum abundance is 10$^{-8}$
HNO: constant abundance of 5$\times$10${-11}$
HCS$^+$: 10$^{-11}$
OCS: constant abundance of 10$^{-9}$
H$_2$CO: 1.5$\times$10$^{-9}$ decreased by a factor of 40 at radii less than 8250au (Young et al 2004)
CS:  3$\times$10$^{-9}$ decreased by a factor of 10,000 at radii less than 6700au (Tafalla, santiago-garcia and myers 2006)
CO: as the H2O profile from ??? scaled so that the maximum abundance is CO maximum\newline

-describe the RT used (LIME) 
LIME, the radiative transfer program used, calculates line intensities based on a weighted sample of randomly chosen points in a continous 3d model. The method of selecting these points is given in the gridding section. At each of these points the density of the main collision partner (in this case H$_2$), gas and dust temperatures, velocity, molecular abundances and turbulent velocity and taken from the model. These points are then smoothed by Lloyds algorithm (Lloyd 1982) in order to minimise the vairiation in distance between points whilst keeping the same underlying distribution. These points are then connected by Delaunay triangulation and it is down these paths that photons are restricted to propagating. The levels of molecules in question are then  calculated at each of these points from collional and radiative (de)excitation and the local radiation field is calculated. This is repeated 20 times with the populations of each level converging towards a single value. \newline

@@

In order to construct the grid, points are randomly selected from the volume being simulated then compaired against a reference point. Grid points are selected at random in cylindrical co-ordinates, linearly spaced in z and $\phi$ and logarithmicly spaced in r. For each point to be selected a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold. After selection of random co-ordinates the Hydrogen density and molecular density at the point (n and m) are compaired against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$). If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use, if not then another r,$\phi$,z co-ordinte is selected. The weighting function and gridding functions were selected empiricly to sample both the all scales while ensuring the majority of the points went into the inner disc which is the region of interest. 20\% of these points are forced to be at radii greater than $\sqrt{R_{min}R_{max}}$ (where $R_{min}$ and $R_{max}$ are the inner and outer radius of the model) in order to stop too many of the selecected points clustering in the high density disc and leaving the envelope undersampled. In addiation to this method of selection 5\% of the points are lineraly distributed in x, y and z with no bias with regards to density or abundance. This provides a minimum level of sampling for the large low density regions in the outer parts of the simulated volume. See figure 5 for example of the points distribution in r, z.

@@

Figures showing the RT results in a few molecules/transitions (CO, HCO$^+$, HCN, OCS, H2CO, NH3 --- maybe H2O,H2$^{18}$O [to try first]) (Note the moment 1 and 0 map were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in the some PV diagrams as the strong absorption feature at all positions around zero velocity, mom1maps are shown with a cutoff of 1/1000 of the peak emission/apsorption value)
\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_contSub.png}

@@

@@

@@

Figure showing different inclinations  
Figure showing different transitions of the same molecule (e.g. CO(1-0), ...(7-6) , OCS,  H2CO ) for same inclination but in different disks (Boley et al. and the smooth disk)

>>>>

 \caption{enevlope model with temp and dust temp (red, green) in kelvin, log number density (blue) in cm$^{-3}$ and inward velocity$\times$100 (cyan) in m$\,$s$^{-1}$}
\end{figure}

@@

-describe the chemistry  - refer to Ilee et al. which have been taken as input to the rad transf (RT) code
Chemical abundances in the disc were taken from Ilee et. al (2011) which followed the changes of chemical abundances of trace particles moving through the disc as it evolved. The abundances of 125 speices related by 1334 reactions were followed through the time evoltion of the disc. These abundances were interpolated onto a 51$^3$ grid covering the disc with cells of size 2.2$\times$2.2$\times$0.22$\,$au. Abundances in the envelope model were as follows:\newline

(tableify this?)\newline
HCO$^+$: as the H2O profile from (find out where L1544 H2O profile is from) scaled so that the maximum abundance is 10$^{-8}$\newline
HNO: constant abundance of 5$\times$10${-11}$\newline
HCS$^+$: 10$^{-11}$\newline
OCS: constant abundance of 10$^{-9}$\newline
H$_2$CO: 1.5$\times$10$^{-9}$ decreased by a factor of 40 at radii less than 8250au (Young et al 2004)\newline
CS:  3$\times$10$^{-9}$ decreased by a factor of 10,000 at radii less than 6700au (Tafalla, santiago-garcia and myers 2006)\newline
CO: as the H2O profile from ??? scaled so that the maximum abundance is CO maximum\newline\

-describe the RT used (LIME) 
LIME (Brinch 2011), the radiative transfer program used, calculates line intensities based on a weighted sample of randomly chosen points in a continous 3d model. The method of selecting these points is given in the gridding section. At each of these points the density of the main collision partner (in this case H$_2$), gas and dust temperatures, velocity, molecular abundances and turbulent velocity and taken from the model. These points are then smoothed by Lloyds algorithm (Lloyd 1982) in order to minimise the vairiation in distance between points whilst keeping the same underlying distribution. These points are then connected by Delaunay triangulation and it is down these paths that photons are restricted to propagating. The levels of molecules in question are then  calculated at each of these points from collional and radiative (de)excitation and the local radiation field is calculated. This is repeated 20 times with the populations of each level converging towards a single value. \newline

@@

In order to construct the grid, points are randomly selected from the volume being simulated then compaired against a reference point. Grid points are selected at random in cylindrical co-ordinates, linearly spaced in z and $\phi$ and logarithmicly spaced in r. For each point to be selected a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold. After selection of random co-ordinates the Hydrogen density and molecular density at the point (n and m) are compaired against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$). If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use, if not then another r,$\phi$,z co-ordinte is selected. The weighting function and gridding functions were selected empiricly to sample both the all scales while ensuring the majority of the points went into the inner disc which is the region of interest. 20\% of these points are forced to be at radii greater than $\sqrt{R_{min}R_{max}}$ (where $R_{min}$ and $R_{max}$ are the inner and outer radius of the model) in order to stop too many of the selecected points clustering in the high density disc and leaving the envelope undersampled. In addiation to this method of selection 5\% of the points are linearly distributed in x, y and z with no bias with regards to density or abundance. This provides a minimum level of sampling for the large low density regions in the outer parts of the simulated volume. See figure 5 for example of the points distribution in r, z.

@@

Figures showing the RT results in a few molecules/transitions (CO, HCO$^+$, HCN, OCS, H2CO, NH3 --- maybe H2O,H2$^{18}$O [to try first]) (Note the moment 1 and 0 map were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in the some PV diagrams as the strong absorption feature at all positions around zero velocity, mom1maps are shown with a cutoff of 1/1000 of the peak emission/apsorption value)

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_contSub.png}

@@

These syntetic images of the CO 3-2 line at 345.8$\,$GHz. As the upper level for this line is at 33$\,$K above the ground state this transition should be excited through out disc. CO line will be thick so this is only mapping the outer regions of the disc. Spiral structure can be seen

@@

The OCS lines in alma band 7 (22-21 through 30-29) with upper energy levels between 161 and 271 K above the ground state provide a way to trace hot shocked gas in spiral arms without resolving structure.

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imagesmoothedOCS_28-27_30deg_contSub.png}

 \caption{SmoothedOCS 28-27 Continuum subtracted mom0}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imagesmoothedOCS_28-27_30deg_mom1.png}

 \caption{SmoothedOCS 28-27 mom1map}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imagesmoothedOCS_28-27_30deg_PV_centre.png}

In comparison to the model with spiral arms the absorbtion and emission from this smoothed model is far weaker.

gdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfd gfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdf gfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsg fsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfds

 \caption{SmoothedOCS 28-27 PV through centre}
\end{figure}

@@

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageHCOp_1-0_30deg_contSub.png}

 \caption{HCO$^+$ 1-0 Continuum subtracted mom0}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageHCOp_1-0_30deg_mom1.png}

 \caption{HCO$^+$ 1-0 mom1map}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageHCOp_1-0_30deg_PV_centre.png}

 \caption{HCO$^+$ 1-0 PV through centre}
\end{figure}

gdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsg fsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfd gdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgf sgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfd gdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfds

Figure showing different inclinations

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_contSub.png}

 \caption{C18O 3-2 15 deg Continuum subtracted mom0}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_mom1.png}

 \caption{C18O 3-2 15 deg mom1map}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_PV_centre.png}

 \caption{C18O 3-2 PV 15 deg through centre}
\end{figure}

15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_contSub.png}

 \caption{C18O 3-2  30 deg Continuum subtracted mom0}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_mom1.png}

 \caption{C18O 3-2 30 deg mom1map}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_PV_centre.png}

 \caption{C18O 3-2 30 deg PV through centre}
\end{figure}

30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_contSub.png}

 \caption{C18O 3-2 45 deg Continuum subtracted mom0}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_mom1.png}

 \caption{C18O 3-2 45 deg mom1map}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_PV_centre.png}

 \caption{C18O 3-2 45 deg PV through centre}
\end{figure}

45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_contSub.png}

 \caption{C18O 3-2 60 deg Continuum subtracted mom0}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_mom1.png}

 \caption{C18O 3-2 60 deg mom1map}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_PV_centre.png}

 \caption{C18O 3-2 60 deg PV through centre}
\end{figure}

60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_contSub.png}

 \caption{C18O 3-2 75 deg Continuum subtracted mom0}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_mom1.png}

 \caption{C18O 3-2 75 deg mom1map}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_PV_centre.png}

 \caption{C18O 3-2 75 deg PV through centre}
\end{figure}

75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg

Figure showing different transitions of the same molecule (e.g. CO(1-0), ...(7-6) , OCS,  H2CO ) for same inclination but in different disks (Boley et al. and the smooth disk)
